The brightness and spatial distributions of terrestrial radio sources

### 2012-12-19 articles/Article-RFI-distribution/article-rfi-distribution.tex
Add authors Wim and Benedetta

\author[A.~R.~Offringa et al.]{
  A.~R.~Offringa$^{1,2}$\thanks{E-mail:
\url{offringa@mso.anu.edu.au}},
  A.~G.~de~Bruyn$^{2,3}$,
   and S.~Zaroubi$^{2}$\\
$^{1}$Australian National University, RSAA Mt. Stromlo Observatory, Cotter Road, Weston Creek ACT 2611, Australia\\
$^{2}$University of Groningen, Kapteyn Astronomical Institute, PO Box 800, 9700 AV Groningen, The Netherlands\\
$^{3}$ASTRON, PO Box 2, 7990 AA Dwingeloo, The Netherlands
}

>>>>

\author[A.~R.~Offringa et al.]{
  A.~R.~Offringa$^{1,2}$\thanks{E-mail:
\url{offringa@mso.anu.edu.au}},
  A.~G.~de~Bruyn$^{2,3}$,
   S.~Zaroubi$^{2}$,
   W.~Brouw$^{2,3}$,
   B.~Ciardi$^{4}$\\
$^{1}$Australian National University, RSAA Mt. Stromlo Observatory, Cotter Road, Weston Creek ACT 2611, Australia\\
$^{2}$University of Groningen, Kapteyn Astronomical Institute, PO Box 800, 9700 AV Groningen, The Netherlands\\
$^{3}$ASTRON, PO Box 2, 7990 AA Dwingeloo, The Netherlands\\
$^{4}$Max-Planck Institute for Astrophysics, Karl-Schwarzschild-Strasse 1, 85748 Garching bei M\"unchen, Germany.
}
